---
title: "Problem 1"
author: "A. J. Rominger"
date: "4/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

If we list all the natural numbers below 10 that are multiples of 3 or 5, we get 3, 5, 6 and 9. The sum of these multiples is 23. Find the sum of all the multiples of 3 or 5 below 1000.

## My first answer in base python

```{python}
def under1000(x):
    maxPos = 999 // x
    allPos = list(range(1, maxPos + 1))
    
    for i in list(range(len(allPos))):
        allPos[i] = allPos[i] * x
    
    return(allPos)

print(sum(list(set(under1000(3) + under1000(5)))))
```


## My answer using `numpy`

```{python}
import numpy as np

def under1000(x):
    maxPos = 999 // x
    allPos = np.array(range(1, maxPos + 1))
    return(np.multiply(allPos, x))

print(sum(np.unique(np.append(under1000(3), under1000(5)))))
```


## Base python solution from ebgreen

```{python}
result = 0

for i in range(1,1000):
    if i % 3 == 0 or i % 5 == 0:
        result = result + i

print(result)
```

## Slick python solution using list comprehension from johanlindberg

```{python}
result = sum([x for x in range(1000) if x % 3== 0 or x % 5== 0])
print(result)
```

## Another slick answer using lambda functions from drigz

```{python}
result = reduce(lambda x,y: x+y, filter(lambda n: n%3==0 or n%5==0, range(1000)))
print(result)
```


## I clearly have an R accent

```{r}
sum(unique(c((1:floor(999 / 3)) * 3, (1:floor(999 / 5)) * 5)))
```
